%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV for A4 paper format
% XeLaTeX Template
% Version 1.0
%
% A4 version author:
% Marvin Frommhold (depressiverobot.com)
% https://github.com/depressiveRobot/friggeri-cv-a4
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Options
% 'print': remove colors from this template for printing
% 'nocolor' to disable colors in section headers
\documentclass[nocolors]{friggeri-cv-a4}
\hypersetup{
     colorlinks   = true,
     citecolor    = gray,
     linkcolor    = green,
     urlcolor     = blue
}  
\addbibresource{bibliography.bib} % Specify the bibliography file to include publications
\usepackage[english]{babel}
\usepackage{multicol}
\setlength{\multicolsep}{3.0pt plus 1.0pt minus 0.75pt}
\usepackage{enumitem}
\setlist{noitemsep}
\setlist{nosep}

\begin{document}
\header{Mario Román}{}{MSc Mathematics and Foundations of Computer Science} % Your name and current job title/field

\begin{aside} % In the aside, each new line forces a line break
  \section{Contact}\\
  Mario Román García\\
+34 693 833838\\
\href{mailto:mromang08@gmail.com}{mromang08@gmail.com}
\href{https://mroman42.github.io}{mroman42.github.io}
\href{https://www.linkedin.com/in/mario-roman}{linkedin:mario-roman}
\section{References}\\
Carmen Constantin\\
\textit{University of Oxford}\\
\href{mailto:i.m.carmen@gmail.com}{i.m.carmen@gmail.com}\\
\quad\\
\href{https://scholar.google.com/citations?user=gvq9UmMAAAAJ&hl=en&oi=ao}{Pedro García-Sánchez}\\
\textit{University of Granada}\\
\href{mailto:pedro@ugr.es}{pedro@ugr.es}\\
\quad\\
\href{https://scholar.google.com/citations?user=HULIk-QAAAAJ&hl=en&oi=sra}{Francisco Herrera}\\
\textit{University of Granada}\\
\href{mailto:herrera@decsai.ugr.es}{herrera@decsai.ugr.es}\\
\quad\\



\section{Languages}\\
\textit{Spanish (native)\\
English (C2) \\
Italian (fluent)}
\section{Programming}
{\small Experience in \textbf{Haskell},
  the proof assistants \textbf{Agda} and \textbf{Coq},
  and imperative programming in \textbf{C++}.
}

\section{Software}\\
{\small Technical knowledge of \textbf{Gnu/Linux},
  \textbf{Emacs} and \textbf{LaTeX}.
}
\end{aside}


\section{Education}

\begin{entrylist}

%------------------------------------------------

\entry{2018-2019}{{\normalfont \textbf{MSc. Mathematics} }{\normalfont \textbf{and Foundations of Computer Science}}}
  {}
  {\href{https://www.ox.ac.uk/admissions/graduate/courses/msc-mathematics-and-foundations-computer-science?wssl=1}
    {\normalsize{University of Oxford}} \\ \emph{Expected graduation in September 2019. \\ MSc. Dissertation on Profunctor optics (supervisor: \href{https://www.cs.ox.ac.uk/people/jeremy.gibbons/}{Jeremy Gibbons})} {\scriptsize
    \begin{multicols}{2}
      \begin{itemize}[topsep=0pt]
      \item Categories, Proofs (95/100), Constantin
      \item Homological Algebra (85/100), Henriques
      \item Quantum Comp. Sci. (81/100), Coecke
      \item Category Theory (91/100), Kirwan
      \item Categorical Quantum (95/100), Vicary
      \item Distributional Models (90/100), Coecke
      \end{itemize}
    \end{multicols}
  }}
  
  
\entry{2012-2018}{Bachelor degree in Mathematics}
{\href{http://www.ugr.es/en/}{University of Granada}}
{\emph{Emphasis in abstract algebra.} Grade Point Average: 9.55/10.
  { 
    % \scriptsize
  % \begin{multicols}{2}
  %   \begin{itemize}[topsep=0pt]
  %   \item Calculus
  %   \item Geometry, linear algebra
  %   \item Numerical methods
  %   \item Probability
  %   \item Algebra
  %   \item Analysis and measure theory
  %   \item Topology
  %   \item Non-euclidean geometry
  %   \item Algebraic topology
  %   \item Galois theory
  %   \item Mathematical modelling
  %   \item Statistical inference
  %   \item Curves and surfaces
  %   \item Differential equations
  %   \item Number theory, criptography
  %   \item Computational algebra
  %   \item Modern algebra
  %   \item Logic, discrete mathematics
  %   \end{itemize}
  % \end{multicols}
  }
}

\entry{2012-2018}{Bachelor degree in Computer Science}
{\href{http://www.ugr.es/en/}{University of Granada}}
{\emph{Emphasis in computation.} Grade Point Average: 9.35/10 \\ \\
  { \textbf{Bachelor's thesis. Category theory and lambda calculus.} \\
    \emph{Award to the best bachelor's thesis in Mathematics-related areas of the University of Granada (2017-18). \\
    Advisors: \href{https://scholar.google.es/citations?user=gvq9UmMAAAAJ&hl=en&oi=ao}{Pedro A. García-Sánchez}.}
    % \scriptsize
  %   \begin{multicols}{2}
  %   \begin{itemize}[topsep=0pt]
  %   \item C++ Programming
  %   \item System administration
  %   \item Computer architecture
  %   \item Operative systems
  %   \item Algorithms
  %   \item Data structures
  %   \item Object-oriented programming
  %   \item Computability theory
  %   \item Automata and languages
  %   \item Software engineering
  %   \item Information theory
  %   \item Functional programming
  %   \item Databases
  %   \item Computer graphics
  %   \item Artificial intelligence
  %   \item Metaheuristics
  %   \end{itemize}
  % \end{multicols}
  }
  
} 

\entry{2012-2018}{High School}
{\href{http://www.juntadeandalucia.es/averroes/centros-tic/18700037/helvia/sitio/}{IES Soto de Rojas}}
{\emph{Emphasis on Science.} Grade Point Average: 10/10
  {
  } 
}

\entry{2015-2018}{Courses and conferences}{}{Attended: {\small
    \begin{itemize}[topsep=0pt]
    \item{\href{http://events.cs.bham.ac.uk/syco/2/}{SYCO 2 (Strathclyde)} and \href{http://events.cs.bham.ac.uk/syco/3/}{SYCO 3 (Oxford)}, on applied category theory.}
    \item{\href{https://homalg-project.github.io/capdays-2018/program/}{CAP Days - Siegen}, on computable homological algebra and categories.}
    \item{\href{https://unimath.github.io/bham2017/}{School on Univalent Mathematics 2017} and \href{https://unimath.github.io/bham2019/}{2019} - Univ. Birmingham.}
    \item{\href{https://sites.google.com/view/summerschool2017-eutypes/program}{EUTypes Summer School}, on Homotopy type theory, Agda and Coq.}
    \item{\href{https://sites.google.com/unizar.es/affine-group-schemes-seminar/inicio}{Seminar on Affine group schemes}, Hopf algebras and algebroids.}
    \item{\href{http://parles.upf.edu/llocs/esslli/welcome-esslli-2015}{ESSLLI-Barcelona}, on Logic, Languages and Computation.}
    \item{\href{http://www.lambda.world/}{Lambda World}, on functional programming.}
      \item{\href{http://www.ugr.es/~orientamat/}{LaTeX course - OrientaMat}, volunteering as \textit{teaching assistant}.}
    \end{itemize}
  }
}

\entry{2008-2012}{\href{http://thales.cica.es/estalmat/}{Estalmat}}{\href{http://www.unia.es/}{University of Granada, Spain}}{A project to detect and stimulate the precocious mathematical talent.}

% \entry{2014--2016}{Programming conferences \& courses}{}
% { \emph{\href{http://www.lambda.world/}{Lambda World}}, Cádiz, 2016 \\
%   \emph{\href{http://parles.upf.edu/llocs/esslli/welcome-esslli-2015}{ESSLLI. Logic, Languages and Computation}}, Barcelona, 2015 \\
%   \emph{\href{http://sci2s.ugr.es/otherCourses/CienciaDatosBigData}{Data Science and Big Data}}, \href{http://www.unia.es/}{International University of Andalucía}, 2014
% }

\end{entrylist}


 \section{Publications}

 \begin{entrylist}
   \entry{2018}{Mikrokosmos: an educational lambda calculus interpreter (\href{https://jose.theoj.org/papers/10.21105/jose.00029}{pdf})}{}
   {
     \textit{Mario Román} \\
     DOI: \href{https://jose.theoj.org/papers/10.21105/jose.00029}{10.21105/jose.00029} \\
     The Journal of Open Source Education.
   }
   
   \entry{2016}{A comparison of implementations of basic evolutionary algorithm operations in different languages}{}
   {
     \textit{J.J. Merelo-Guervós, I. Blancas, P. Castillo, G. Romero, V. Rivas, M. García-Valdez, A. Hernández-Aguila, M. Román.} \\
     DOI: 10.1109/CEC.2016.7743980 \\
     Conference: \href{http://ieeexplore.ieee.org/document/7743980/2016}{IEEE Congress on Evolutionary Computation (CEC)}
   }

   \entry{2019}{Discokitty, an implementation of the DisCoCat framework}{}
   {
     \textit{Mario Román.} \\
     In progress. To be submitted to \href{https://sites.google.com/view/semspace2019/home}{SemSpace2019}. \\
     
     }
 \end{entrylist}

\newpage
\subsection{Research experience}

\begin{entrylist}
  \entry{2019-ongoing}{Applied Category Theory School 2019}{\href{https://www.cs.ox.ac.uk/ACT2019/}{ACT 2019}}
  { Accepted into the project on
    \textit{Traversal optics and profunctors}, directed by \textit{\href{https://bartoszmilewski.com/2019/01/05/act2019-school-call-for-participation/}{Bartosz Milewski}}.
  }
  
  \entry{2017-2018}{Collaboration and research Fellowship, department of
    Algebra}{}
  { {\small \textit{Advisor: \href{https://scholar.google.es/citations?user=gvq9UmMAAAAJ&hl=en&oi=ao}{Prof. Pedro A. García-Sánchez}.}} \\
    During my Bachelor's thesis. On the categorical semantics of
    lambda calculus. Studying Martin-Löf type theory as the internal
    language of locally closed cartesian categories. Agda is used to
    provide examples of formalized univalent mathematics.  }

   


\end{entrylist}


% \section{projects}


\subsection{Computer science projects}



\begin{entrylist}
\entry{2016-2018}{Mikrokosmos}
{\href{https://github.com/mroman42/mikrokosmos}{github.com/mroman42/mikrokosmos}}
{\emph{Hackage: \href{https://hackage.haskell.org/package/mikrokosmos}{hackage.haskell.org/package/mikrokosmos}} \\
  An didactic free software λ-calculus interpreter written in Haskell supporting multiple evaluation strategies and exemplifying the Curry-Howard isomorphism.
}
\entry{2014-2015}{GranaSAT Client}
{\href{https://github.com/mroman42/granasatClient}{github.com/mroman42/granasatClient}}
{\emph{Git repository: \href{https://github.com/mroman42/granasatClient}{github.com/mroman42/granasatClient}} \\
  Software for a satellite student experiment for the
  European Space Agency \href{http://rexusbexus.net/}{BEXUS campaign}.
}
\end{entrylist}

\textit{A complete portfolio can be found on
  \href{https://github.com/mroman42}{GitHub}.}
I have made contributions to
\begin{itemize}
\item The \href{https://github.com/UniMath/UniMath}{\textbf{UniMath} Coq library}, by Voevodsky, Greyson, Ahrens et al.
\item \href{https://homalg-project.github.io/CAP_project/CAP/}{\textbf{Categories, Algebra and Programming} GAP package},
  by Gutsche, Posur et al.
\end{itemize}

 
 
\section{Awards and Grants}

\begin{entrylist}

  \entry{2017-2018}{Collaboration Grant (2000€)}{Algebra department,
    University of Granada} {By virtue of which I could develop my
    bachelor's thesis. I administered the deparment servers, developed
    \textit{didactic material} and the \textit{\href{https://github.com/mroman42/mikrokosmos}{Mikrokosmos}}
    interpreter, and assisted in the teaching of the course
    \textbf{"Logic and Programming"} \textit{(\href{http://grados.ugr.es/informatica/pages/infoacademica/guias_docentes/201516/cuarto/ingenieriadelsoftware/complementos/logicayprogramacion/!}{Lógica y programación})}.  }

  \entry{2015-2016}{\href{http://ec.europa.eu/programmes/erasmus-plus/node_en}{Erasmus+ Grant (5442€)}}{\href{http://www.unimi.it/ENG/}{University of Milan}}{
    Exchange student at the
    \href{http://www.unimi.it/ENG/}{University of Milan} for a year. Studying at the
    \href{http://www.di.unimi.it/ecm/home/didattica/international-studies/activity/courses}{department of computer science}.
  }
  
\entry{2012--2013}{International Mathematical Olympiad, \href{http://www.imo-official.org/}{IMO} (\textasciitilde{} 1100€)}
{Argentina}
{National \emph{Gold (2012) \& Silver (2011) Medals} and an
  \href{https://www.imo-official.org/team_r.aspx?code=ESP&year=2012}{International} \emph{Honourable mention} (2012).}


\end{entrylist}

\section{Interests}

I am passionate about \textbf{category theory} and \textbf{functional
  programming} but also about type theory and the applications of
category theory. I also am actively involved in the
\textbf{divulgation of mathematics} and computer science at a
universitary level.

\begin{entrylist}
  \entry{2014--2018}{LibreIM}{\href{http://libreim.github.io/}{libreim.github.io/}}
  { Founder and coordinator of a
    \href{http://libreim.github.io/}{community} of Math\&CS students.
    I am the main contributor to our
    \href{http://libreim.github.io/blog/}{blog} and the organizer of
    weekly
    \href{http://libreim.github.io/dgiim/awesome/seminars/}{seminars}
    where I have organized seminars about
    \href{https://github.com/libreim/haskell}{Haskell},
    \href{https://github.com/libreim/introCategorias/blob/master/categorias.pdf}{Category
      theory} and
    \href{https://github.com/mroman42/libreim-constructiva/blob/master/constructiva.pdf}{Constructive mathematics}, among other topics.}
\end{entrylist}
\end{document}
